---
title: "MATH 237 SPring Break Activity"
author: "Aubree, Nick & Chandra"
date: "3/10/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
FullertonHousing = read.csv("~/m237/FullertonHousing.csv", header = TRUE)
attach(FullertonHousing)
```

Problem 1: 
In the Fullerton Housing data set, let PRICE be the response and consider BEDS, BATHS, SQUARE_FEET, and YEAR-Built to be your predictors. First, fit a multiple linear regression model to this data will all four predictors in the model. 

```{r}
four.predictors= lm(PRICE~ BEDS+ BATHS+ SQUARE_FEET +YEAR_BUILT, data=FullertonHousing)
four.predictors
summary(four.predictors)
```
This model does not seem to fit the data accurately. There is a high standard error of $127,200 with 190 degrees of freedom. This is probably not the best data to choose. 


Problem 2: Consider the four possible models that have only one predictor. Using the 5-fold cross validation technique, compare RMSE of the four models. Which one is a better model? 

This will perform 5-fold method for BEDS. 

```{r}
library(caret)

Fullerton=data.frame(FullertonHousing)

ctrl <- trainControl(method = "cv", number = 5)
model.beds <- train(PRICE~ BEDS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.beds)

```

This will perform 5-fold method  for BATHS. 
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.baths <- train(PRICE~ BATHS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.baths)
```

This will perform 5-fold method for SQUARE_FEET.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.square.feet <- train(PRICE~ SQUARE_FEET, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.square.feet)
```

Lastly, this will perform five-fold method on YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.year.built <- train(PRICE~ YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.year.built)
```

After reviewing all Residual Mean squared errors, the best model is formed under square feet. The model based on square feet has the lowest RMSE. 

Problem 3: Insert problem 
