---
<<<<<<< HEAD
title: "MATH 237 Spring Break Activity"
author: "Aubree Krager, Chandra Lindy, and Nicholas Noel"
date: "April 4th, 2022"
=======
title: "MATH 237 SPring Break Activity"
author: "Aubree, Nick & Chandra"
date: "3/10/2022"
>>>>>>> 20a5ca8 (Updated title - Pull request example)
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
FullertonHousing = read.csv("~/m237/FullertonHousing.csv", header = TRUE)
attach(FullertonHousing)
```

__Problem 1__:
In the Fullerton Housing data set, let PRICE be the response and consider BEDS, BATHS, SQUARE_FEET, and YEAR-Built to be your predictors. First, fit a multiple linear regression model to this data will all four predictors in the model. 

```{r}
four.predictors= lm(PRICE~ BEDS+ BATHS+ SQUARE_FEET +YEAR_BUILT, data=FullertonHousing)
four.predictors
summary(four.predictors)
```
This model does not seem to fit the data accurately. There is a high standard error of $127,200 with 190 degrees of freedom. This is probably not the best data to choose. 


__Problem 2__: Consider the four possible models that have only one predictor. Using the 5-fold cross validation technique, compare RMSE of the four models. Which one is a better model? 

This will perform 5-fold method for BEDS. 

```{r}
Fullerton=data.frame(FullertonHousing)

ctrl <- trainControl(method = "cv", number = 5)
model.beds <- train(PRICE~ BEDS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.beds)
```
The reported log(RMSE) is 12.19813.

This will perform 5-fold method for BATHS. 
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.baths <- train(PRICE~ BATHS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.baths)
```
The reported log(RMSE) is 12.2937.

This will perform 5-fold method for SQUARE_FEET.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.square.feet <- train(PRICE~ SQUARE_FEET, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.square.feet)
```
The reported log(RMSE) is 11.79194.

Lastly, this will perform five-fold method on YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.year.built <- train(PRICE~ YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.year.built)
```
The reported log(RMSE) is 12.57814.

After reviewing all RMSE's, the best model is formed under the variable SQUARE_FEET. The model based on SQUARE_FEET has the lowest RMSE. 

__Problem 3__: Consider all six models that have only two predictors. For example lm(PRICE~BEDS+BATHS). Using the 5-fold cross validation technique, compare the RMSE of the six models. Which one is a better model?


The following model has the predictors BEDS and BATHS.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BEDBATH <- train(PRICE~ BEDS + BATHS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDBATH)
```
The reported log(RMSE) for this model is 12.16248.

The following model has the predictors BEDS and SQUARE_FEET. 
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BEDFOOT <- train(PRICE~ BEDS + SQUARE_FEET, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDFOOT)
```
The reported log(RMSE) for this model is 11.7949.

The following model has the predictors BEDS and YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BEDBUILT <- train(PRICE~ BEDS + YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDBUILT)

```
The reported log(RMSE) for this model is 12.2393.

The following model has the predictors BATHS and SQUARE_FEET.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BATHFOOT <- train(PRICE~ BATHS + SQUARE_FEET, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BATHFOOT)

```
The reported log(RMSE) for this model is 11.77536.

The following model has the predictors BATHS and YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BATHBUILT <- train(PRICE~ BATHS + YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BATHBUILT)
```
The reported log(RMSE) for this model is 12.27687.

The following model has the predictors SQUARE_FEET and YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.SQUAREBUILT <- train(PRICE~ SQUARE_FEET + YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.SQUAREBUILT)
```
The reported log(RMSE) for this model is 11.7563.

With this group the best model considers the varaibles SQUARE_FEET and YEAR_BUILT. This model has the lowest RMSE. 


__Problem 4__: Consider all four possible models that have three predictors. For example lm(PRICE~BEDS+BATHS+SQUARE_FEET). Using the 5-fold cross validation technique compare the RMSE of the four models. Which one is a better model?

The following model has the predictors BEDS, BATH, and SQUARE_FEET.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BEDBATHFEET <- train(PRICE~ SQUARE_FEET + BEDS + BATHS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDBATHFEET)
```
The reported log(RMSE) is 11.75978.

The following model has the predictors BATHSM, SQUARE_FEET, and YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BATHFEETBUILT <- train(PRICE~ SQUARE_FEET + YEAR_BUILT + BATHS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDBATHFEET)
```
The reported log(RMSE) is 11.75978.

The following model has the predictors BEDS, SQUARE_FEET, and YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BEDBUILTFEET <- train(PRICE~ SQUARE_FEET + BEDS + YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDBUILTFEET)
```
The reported log(RMSE) is 11.75699.

The following model has the predictors BEDS, BATHS, and YEAR_BUILT.
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.BEDBATHBUILT <- train(PRICE~ YEAR_BUILT + BEDS + BATHS, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.BEDBATHBUILT)
```
The reported log(RMSE) is 12.18601.

With this group the best model considers the varaibles BEDS, SQUARE_FEET, and YEAR_BUILT. This model has the lowest RMSE. 

__Problem 5__: Consider the only model that has four predictors. Using the 5-fold cross validation technique, calculate the RMSE of that model. 

This models considers the variables SQUARE_FEET, BEDS, BATHS, and YEAR_BUILT. 
```{r}
ctrl <- trainControl(method = "cv", number = 5)
model.all <- train(PRICE~ SQUARE_FEET + BEDS + BATHS + YEAR_BUILT, 
               data = FullertonHousing, method = "lm", trControl = ctrl)

print(model.all)
```
The reported log(RMSE) is 11.75016.


__Problem 6__: Between all the models you fit to this data in parts  2-5 which one has the lowest RMSE or the best goodness of fit? Is that surprising?

The best model is the model that examines all four variables. This model has the lowest RMSE. This is not suprising because it takes the most variables into consideration. 

